Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-08 RR_manuscript/Draft_RR.Rmd
♻️ - edit results in draft

## Sample description

@@

## Meta analysis

```{r load-meta-analysis}
meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))

@@

compelling_count <- table(post_meta$compelling)
```

@@

<!-- TODO: discuss between-team variability -->
<!-- TODO: This is more like between-model variability -->

As explained in the **Methods** section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e. the standard deviation of the group-level effect of team `(!!! we have now model_id)` returned by the meta-analytic model.

According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95% credibility.
This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.

@@

### Estimating the crowd sourced effect size

The Bayesian random effects model estimates the range of probable values of the standardized effect size between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` (95\% CrI, mean = `r round(meta_intercept[1],3)`)
In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is `r round(meta_intercept[1],2)` standard deviations above zero. This outcome thus estimates that atypical word combinations have `r round(meta_intercept[1],2)` standard deviations higher acoustic values (e.g. duration, f0 etc,) than typical word combinations.

<!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES (ALTERNATIVELY IN IQ VALUES).-->

This is not only an extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but there is also much uncertainty around this estimate and the range of probably values includes zero. 
Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not zero to begin with. 
Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but if there is an effect of typicality, it is very small.
Moreover, this population estimate is half the size of the estimated standard deviation between different models <!-- TR: EXTRACT BETA AND CRIS).-->

(ref:meta_plot1) illustrates the estimated model outputs for all submitted models according to size. 
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g. longer duration, higher f0, etc.).
Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).

@@

```{r 'plot-meta1', echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
knitr::include_graphics(here::here("./plots/meta_plot1.png"), error = FALSE)
```

### Can we predict the estimate?
After assessing the variability across models, we now turn toward estimating the impact of a series of predictors on the analysts' model estimates.
There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?

@@

```{r 'plot-meta2', echo = FALSE, fig.cap="(ref:metaPlot2)", out.width="100%"}
knitr::include_graphics(here::here("./plots/alltogether.png"), error = FALSE)
```

@@

## Caveats
Our study has several limitations that need to be considered when evaluating our results. 
First, there is potential for bias. The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods. We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field. 
This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom. 
We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable. 
However, our results should be independently re-analysed and replicated using a different research question.
Moreover, our sample is an opportunity sample. 
We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
This is particularly important for the predictor evaluation.
Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty. 
This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: *Do speakers acoustically modify utterances to signal atypical word combinations?* 
Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects [@auspurg2021has]. 
However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see @scheel2022most) a common phenomenon. 
For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic]. 
<!-- TR: still adding this? Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did). -->
- We have not investigated researcher positionality, which is known to be an important factor.  <!-- TR:@stef explain here -->

>>>>

## Descriptive statistics

@@

## Meta-analytic estimation

<!-- TODO: add background info and use consistent terminology -->
This section deals with the meta-analytic analysis of the results submitted by the teams.
We first report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.

```{r load-meta-analysis}
# Preregistered ----
meta_bm_prereg <- readRDS(here("./data/meta_analysis/meta_bm_prereg.rds"))

meta_intercept_prereg <- fixef(meta_bm_prereg)
meta_random_prereg <- ranef(meta_bm_prereg)

# wrangle by hand 
post_meta_prereg <- meta_bm_prereg %>%
  spread_draws(b_Intercept, r_animal[team,]) %>%
  mutate(team_mean = b_Intercept + r_animal) %>% 
  group_by(team) %>% 
  dplyr::summarise(post_mean = mean(team_mean),
            lower95 = quantile(team_mean, probs = .025),
            higher95 = quantile(team_mean, probs = .975)
            ) %>% 
  # this basically needs to be fed by whether or not the authors considered there to be an effect
  mutate(compelling = as.factor(case_when(lower95 > 0 ~ "negative",
                                          higher95 < 0 ~ "positive",
                                          TRUE ~ "not compelling")))

compelling_results_prereg <- post_meta_prereg %>% 
  count(compelling) %>% 
  summarise(prop = n / sum(n))

compelling_count_prereg <- table(post_meta_prereg$compelling)

# Model ID ----

meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))

@@

compelling_count <- table(post_meta$compelling)

# Nested ----

meta_bm_nest <- readRDS(here("./data/meta_analysis/meta_bm_nest.rds"))

meta_intercept_nest <- fixef(meta_bm_nest)
meta_random_nest <- ranef(meta_bm_nest)

# wrangle by hand 
post_meta_nest <- meta_bm_nest %>%
  spread_draws(b_Intercept, `r_animal:model_id`[model,]) %>%
  mutate(model_mean = b_Intercept + `r_animal:model_id`) %>% 
  group_by(model) %>% 
  dplyr::summarise(post_mean = mean(model_mean),
            lower95 = quantile(model_mean, probs = .025),
            higher95 = quantile(model_mean, probs = .975)
            ) %>% 
  # this basically needs to be fed by whether or not the authors considered there to be an effect
  mutate(compelling = as.factor(case_when(lower95 > 0 ~ "negative",
                                          higher95 < 0 ~ "positive",
                                          TRUE ~ "not compelling")))

compelling_results_nest <- post_meta_nest %>% 
  count(compelling) %>% 
  summarise(prop = n / sum(n))

compelling_count_nest <- table(post_meta_nest$compelling)
```

@@

As explained in the **Methods** section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e. the standard deviation of the group-level effect of team returned by the meta-analytic model.

According to the meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95% credibility.
This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.

**Non-preregistered**. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
We have run two further non-preregistered meta-analytic models:

1. A model with model ID instead of team as the group-level effect (`(1|model_id)`).
2. A model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id`).

Based on the first non-preregistered model, the group-level standard deviation for model ID is between 0.11 and 0.15 standard units, at 95% credibility.
This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.

As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95% CrI for team in the second non-preregistered model is 0-0.05 standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.

@@

### Meta-analytic intercept

The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
In other words, our best guess is that typical and atypical word combinations might not differ in acoustic measures (e.g. duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.

<!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES, like we do with team variability (ALTERNATIVELY IN IQ VALUES).-->

<!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->

**Non-preregistered**. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
In the first model, the meta-analytic intercept estimate is between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept[1],3)`).
This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95% confidence.
Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
The estimated intercept from the second model (with nested group-level effects) is virtually identical to the first (with only model ID as group-level effect).

(ref:meta_plot1) illustrates the individual model intercepts, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g. longer duration, higher f0, etc.), as mentioned above.
Notably, while the majority of models yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).

@@

```{r plot-meta1, echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
knitr::include_graphics(here::here("./figs/meta_plot1_nest.png"), error = FALSE)
```

## Analytic and researcher-related predictors

After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the estimated intercept.
There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?

@@

```{r plot-meta2, echo = FALSE, fig.cap="(ref:metaPlot2)", out.width="100%"}
knitr::include_graphics(here::here("./figs/alltogether.png"), error = FALSE)
```

@@

## Caveats

Our study has several limitations that need to be considered when evaluating our results. 
First, there is potential for bias. The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods. We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field. 
This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom. 
We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable. 
However, our results should be independently re-analysed and replicated using a different research question.
Moreover, our sample is an opportunity sample. 
We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
This is particularly important for the predictor evaluation.
Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty. 
This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: *Do speakers acoustically modify utterances to signal atypical word combinations?* 
Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects [@auspurg2021has]. 
However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see @scheel2022most) a common phenomenon. 
For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic]. 
<!-- TR: still adding this? Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did). -->
- We have not investigated researcher positionality, which is known to be an important factor.  <!-- TR:@stef explain here -->

### 2022-09-08 RR_manuscript/Draft_RR.tex
♻️ - edit results in draft

\hypertarget{sample-description}{%
\subsection{Sample description}\label{sample-description}}

@@

\hypertarget{meta-analysis}{%
\subsection{Meta analysis}\label{meta-analysis}}

\begin{verbatim}
## Warning: `gather_()` was deprecated in tidyr 1.2.0.
## Please use `gather()` instead.
## This warning is displayed once every 8 hours.
## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

@@

As explained in the \textbf{Methods} section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team \texttt{(!!!\ we\ have\ now\ model\_id)} returned by the meta-analytic model.

According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95\% credibility.
This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.

\hypertarget{estimating-the-crowd-sourced-effect-size}{%
\subsubsection{Estimating the crowd sourced effect size}\label{estimating-the-crowd-sourced-effect-size}}

The Bayesian random effects model estimates the range of probable values of the standardized effect size between -0.01 and 0.04 (95\% CrI, mean = 0.016)
In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is 0.02 standard deviations above zero. This outcome thus estimates that atypical word combinations have 0.02 standard deviations higher acoustic values (e.g.~duration, f0 etc,) than typical word combinations.

This is not only an extremely small effect , but there is also much uncertainty around this estimate and the range of probably values includes zero.
Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not zero to begin with.
Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but if there is an effect of typicality, it is very small.
Moreover, this population estimate is half the size of the estimated standard deviation between different models

(ref:meta\_plot1) illustrates the estimated model outputs for all submitted models according to size.
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.).
Notably, while the majority of models yielded inconclusive results, there are 28 model estimates for which the 95\% credible interval does not contain zero (16\%).

\begin{figure}
\includegraphics[width=1\linewidth]{../plots/meta_plot1} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
\end{figure}

\hypertarget{can-we-predict-the-estimate}{%
\subsubsection{Can we predict the estimate?}\label{can-we-predict-the-estimate}}

After assessing the variability across models, we now turn toward estimating the impact of a series of predictors on the analysts' model estimates.
There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}?

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../plots/alltogether} \caption{(ref:metaPlot2)}\label{fig:plot-meta2}
\end{figure}

@@

It particularly struck us that teams did not follow our instructions to only submit a single effect size.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for (Tukey 1954, Benjamini \& Hochberg 1995).
It also invites bias, leading to the selective reporting of those tests that yield a desirable outcome (Kerr 1998, John et al.~2012, Simmon et al.~2011) while null results remain unreported (Sterling 1959, REF).
Our data suggest that fields that use highly complex raw data such as speech should be particularly cautious when analyzing their data.

@@

The current results point to important barriers for successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
One of the suggested paths forward is for researchers to directly replicate previous study more often {[}\citet{open2015estimating}; REFS, REFS{]}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Well-trained and experienced speech researchers in this study not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as the peer-ratings suggest.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.

@@

In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others (REF).
This enables critical evaluation and robustness checks by other fellow researchers (REF).
Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process {[}e.g., CITE Praat, EMU CITE){]}{]}.

>>>>

\hypertarget{descriptive-statistics-1}{%
\subsection{Descriptive statistics}\label{descriptive-statistics-1}}

@@

\hypertarget{meta-analytic-estimation}{%
\subsection{Meta-analytic estimation}\label{meta-analytic-estimation}}

This section deals with the meta-analytic analysis of the results submitted by the teams.
We first report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.

@@

As explained in the \textbf{Methods} section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team returned by the meta-analytic model.

According to the meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95\% credibility.
This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.

\textbf{Non-preregistered}. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
We have run two further non-preregistered meta-analytic models:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  A model with model ID instead of team as the group-level effect (\texttt{(1\textbar{}model\_id)}).
\item
  A model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id}).
\end{enumerate}

Based on the first non-preregistered model, the group-level standard deviation for model ID is between 0.11 and 0.15 standard units, at 95\% credibility.
This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.

As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0-0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.

\hypertarget{meta-analytic-intercept}{%
\subsubsection{Meta-analytic intercept}\label{meta-analytic-intercept}}

The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.022 and 0.023 standard units (95\% CrI, mean = 0.001).
In other words, our best guess is that typical and atypical word combinations might not differ in acoustic measures (e.g.~duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.

\textbf{Non-preregistered}. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
In the first model, the meta-analytic intercept estimate is between -0.01 and 0.04 standard units (95\% CrI, mean = 0.016).
This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
The estimated intercept from the second model (with nested group-level effects) is virtually identical to the first (with only model ID as group-level effect).

(ref:meta\_plot1) illustrates the individual model intercepts, sorted in ascending order based on their mean.
Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
Notably, while the majority of models yields inconclusive results, there are 25 model estimates for which the 95\% credible interval does not contain zero (15\%).

\begin{figure}
\includegraphics[width=1\linewidth]{../figs/meta_plot1_nest} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
\end{figure}

\hypertarget{analytic-and-researcher-related-predictors}{%
\subsection{Analytic and researcher-related predictors}\label{analytic-and-researcher-related-predictors}}

After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the estimated intercept.
There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}?

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figs/alltogether} \caption{(ref:metaPlot2)}\label{fig:plot-meta2}
\end{figure}

@@

It particularly struck us that teams did not follow our instructions to only submit a single effect size.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep[Tukey 1953,][]{benjamini1995controlling}.
It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.

@@

The current results point to important barriers for successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature {[}e.g., REFERENCE{]}.
One of the suggested paths forward is for researchers to directly replicate previous study more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
The quantitative sciences are in an inference crisis \citep{rotello2015more, starns2019assessing}.
Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as their peer-ratings suggest.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.

@@

In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility (LeBel et al., 2018).
It allows for alternative analyses to establish analytic robustness (Steegen et al., 2016) and strengthens attempts to synthesize evidence via meta-analyses (Nicenboim et al., 2018)
This enables critical evaluation and robustness checks by other fellow researchers (REF).
Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process {[}e.g., CITE Praat, EMU CITE){]}{]}.
